Market Expectations and Mangerial Turnover

### 2024-02-29 paper.qmd
upload the results of the call to an LLM

```{python}
# Read the CSV files
spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
spells2 = pd.read_csv("raw_data/club_manager_histories_df.csv")

@@

```{python}
import numpy as np
def season_to_date(season):
    if pd.isnull(season) or '/' not in season:
        return np.nan

@@

```{python}
# Apply the function only to rows where 'Date' is NaN
mask=spells1['Finish'].isna()
spells1.loc[mask, 'Finish'] = spells1.loc[mask,'contract_expiry'].apply(season_to_date)
#spells1[spells1['Finish'].isna()].value_counts()
spells1['Finish'].isna().value_counts()
```

>>>>

```{python}
# Read the CSV files
import pandas as pd
spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
spells2 = pd.read_csv("raw_data/club_manager_histories_df.csv")

@@

```{python}
import numpy as np
from datetime import datetime 
def season_to_date(season):
    if pd.isnull(season) or '/' not in season:
        return np.nan

@@

```{python}
# Apply the function only to rows where 'Date' is NaN
mask=spells1['Finish'].isna()
spells1.loc[mask, 'Finish'] = spells1.loc[mask,'contract_expiry'].apply(season_to_date)
spells1['Finish'].isna().value_counts()

```
```{python}
#spells1['spell_in_days']=spells1['Finish']-spells1['Start']
#spells1['spell_in_days']
import csv
team_names=spells1['club'].unique()
# Convert the Series to a DataFrame
teams_df = pd.DataFrame(team_names,columns=['TeamName'])
teams_df.to_csv('teams.csv')
```

```{python}
team_names
```
